Data Preparation

### 2019-03-11 Data Preparation.Rmd
Extract course description from course overview

  transmute(
    `Course ID` = manuals %>% map(function(x) x$meta$id) %>% map_chr(extract_code),
    year        = "2017-2018",
    text        = manuals %>% map(content) %>% map_chr(str_c, collapse = " ")
    ) %>%
  print
```

@@

```{r extracting overview, cache = TRUE}
#
# Set up
years <- paste0(2014:2018, "-", 2015:2019)

headers <- c(
  "^Core Courses \\(COR\\)",
  "^Humanities \\(HUM\\)",
  "^Sciences \\(SCI\\)",
  "^Social Sciences \\(SSC\\)",
  "^Skills Trainings? \\(SKI\\)",
  "^Projects? \\(PRO\\)",
  "^Undergraduate Research", "UCM Undergraduate\r\n ? ?Research",
  "Appendix"
  ) %>%
  paste(collapse = "|")

overview_start <- c(
  "COR",
  "HUM", "SCI", "SSC", 
  "SKI", "PRO",
  "UGR", "CAP"
  ) %>% 
  paste(collapse = "|")

@@

#
# main function
extract_overview <- function(page){

  # create tibble to facilitate manipulation
  page %>% 
    tibble(page = .) %>%

@@

    # paste current page and following page (`lead(page)`) if overview is two page long
    transmute(
      text        = list(page, lead(page)) %>% pmap_chr(paste_if_two_page_overview),
      `Course ID` = text %>% extract_code
      )

@@

  # add the year to each observation to keep track of the evolution of the catalogue oevr time
  map2(
    .y = years,
    .f = function(x, year) x %>% mutate(year = year)
    ) %>%

@@

# Setup
symbol_to_line <- c("\r\n", "\n") %>% paste(collapse = "|")
start_descrip  <- c("^Description", "^Course Description") %>% paste(collapse = "|")
end_descrip    <- c("^Recommended Literature", "^ ?Required Litera", "^ ?Literature$", "Literature \\(all") %>%  paste(collapse = "|")

# helper functions
split              <- function(string) string %>% str_split(pattern = "\r\n|\n")

is_start_descrip   <- function(x) x %>% str_detect(pattern = start_descrip           )
is_end_descrip     <- function(x) x %>% str_detect(pattern = end_descrip             )
is_end_descrip_bis <- function(x) x %>% str_detect(pattern = "^Instructional format$")

# main function
extract_description <- function(page){

  page %>%
    split %>%
    tibble(line = .) %>%

    mutate(
      is_start_descrip = line %>% is_start_descrip,
      is_end_descrip   = line %>% is_end_descrip
    ) %>%

    mutate(
      is_end_descrip = if_else(any(is_end_descrip), is_end_descrip, line %>% is_end_descrip_bis)
    ) %>%

@@

d_text$overview %>%
  mutate(
    description = overview %>% map(extract_description)
  )
```

>>>>

  transmute(
    `Course ID` = manuals %>% map(function(x) x$meta$id) %>% map_chr(extract_code),
    year        = "2017-2018",
    text        = manuals %>% map(content) %>% map_chr(str_c, collapse = " ")
    ) %>%
  print

rm(read_in_pdfs)
```

@@

```{r extracting overview, cache = TRUE}
#
# Set up

collapse_or <- function(string) string %>% str_c(collapse = "|")

years <- paste0(2014:2018, "-", 2015:2019)

headers <- c(
  "^Core Courses \\(COR\\)",
  "^Humanities \\(HUM\\)",
  "^Sciences \\(SCI\\)",
  "^Social Sciences \\(SSC\\)",
  "^Skills Trainings? \\(SKI\\)",
  "^Projects? \\(PRO\\)",
  "^Undergraduate Research", "UCM Undergraduate\r\n ? ?Research",
  "Appendix"
  ) %>%
  collapse_or

overview_start <- c(
  "COR",
  "HUM", "SCI", "SSC", 
  "SKI", "PRO",
  "UGR", "CAP"
  ) %>% 
  collapse_or

@@

#
# main function
extract_overview <- function(catalogue){

  # create tibble to facilitate manipulation
  catalogue %>% 
    tibble(page = .) %>%

@@

    # paste current page and following page (`lead(page)`) if overview is two page long
    transmute(
      text        = list(page, lead(page)) %>% pmap_chr(paste_if_two_page_overview),
      `Course ID` = text %>% extract_code
      ) %>%
    filter(!is.na(text))

@@

  # add the year to each observation to keep track of the evolution of the catalogue over time
  map2(
    .y = years,
    .f = function(x, year) x %>% mutate(year = year)
    ) %>%

@@

#
# Setup
symbol_to_line <- c("\r\n", "\n") %>% collapse_or
start_descrip  <- c("^Description", "^Course Description") %>% collapse_or
end_descrip    <- c(
  "^Recommended Literature", "^ ?Required Litera", "^ ?Literature$", "Literature \\(all",
  "^Instructional format$"
  ) %>% collapse_or

#
# helper functions
split              <- function(string) string %>% str_split(pattern = "\r\n|\n") %>% .[[1]]

is_start_descrip   <- function(x) x %>% str_detect(pattern = start_descrip           )
is_end_descrip     <- function(x) x %>% str_detect(pattern = end_descrip             )

#
# main function
extract_description <- function(overview){

  overview %>%
  split %>%
  tibble(line = .) %>%

  mutate(
    is_start_descrip = line %>% is_start_descrip,
    is_end_descrip   = line %>% is_end_descrip # several ends (matching literature and instructional format) is ok because we choose the first (cumany)
  ) %>%

@@

d_text$description <- d_text$overview %>%
  mutate(
    text = text %>% map_chr(possibly(extract_description, "ERROR"))
    )
```
